### 2019-01-10 Sections/costs_and_attributes_in_quantum_networks.tex
no message

The \textit{quantum channel capacity} is then defined as
\begin{align}
Q(\mathcal{E}) = \lim_{n \rightarrow \infty} \frac{1}{n} \mathcal{I}_Q(\mathcal{E})^{\otimes n}
\label{eq:quantcohinfo}
\end{align}

@@

>>>>

The \textit{quantum channel capacity} is then defined as
\begin{align}
Q(\mathcal{E}) = \lim_{n \rightarrow \infty} \frac{1}{n} \mathcal{I}_Q(\mathcal{E}^{\otimes n})
\label{eq:quantcohinfo}
\end{align}

@@

We now discuss the quantum capacity for the erasure channel and the amplitude damping channel, both of which the quantum capacities can be calculated.

We recall that the erasure channel acts on a state as follows is  
\begin{align}
\rho \rightarrow (1-\eta) \rho + \eta\ket{e}\bra{e}
\end{align}
\noindent where $\eta$ is the probability of losing the state and $\ket{e}\bra{e}$ is orthogonal to $\rho$. Given a system of dimension $d_A$, For $\eta \in [1/2,1]$, the quantum capacity is zero. For $\eta \in [0,1/2]$, the quantum capacity is $(1-2\eta)\log d_A.$

For an amplitude damping channel with damping parameter $\gamma$, the Kraus operators can be written as
\begin{align}
A_0 = \ket{0}\bra{0} + \sqrt{1-\gamma}\ket{1}\bra{1}, \qquad A_1 = \sqrt{\gamma}\ket{1}\bra{1}.
\end{align}

For $\gamma \in [0,1/2]$,the quantum capacity is equal to
\begin{align}
\max_{p \in [0,1]} h_2 [(1-\gamma)p] - h_2[\gamma_p]
\end{align}
\noindent where $h_2$ represents the binary entropy function. For $\gamma \in [1/2,1]$, the quantum capacity is equal to zero.

Two of the most surprising discoveries of quantum Shannon theory is the \textit{superadditivity} of coherent information for the depolarizing channel, and \textit{superactivation} of quantum capacity, where two channels whose indivicual capacities are zero can be combined to make a channel with non-zero capacity.
